Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 sections/lang.tex
Update on Overleaf.

We include the sketch of our semantics to highlight several key design choices.
%
\teo{Make this true:}
First, we note that the life cycle rules (in combination with the definition rules) prevent programs that read and write to values within a loop except in the narrow circumstance of updates, which cannot even be applied to scalar definitions.
%
Beyond the simple management of iterator state, these rules allow us to effectively analyze the propagation of constants within a loop.
%
We eliminate problems that in a less restrictive language would require alias analysis so that we can tell when a zero or repetitive value read from one tensor is being used in an expression or written to another tensor.
%
These restrictions play a similar role to that of a pure function in Halide~\cite{ragan-kelley_halide_2013}.
%
Second, loops with tensor accesses enter into a looplet system via the Unfurl rule.
%
In this system, repeated structures  (Run) and constant informa

>>>>

We include the sketch of our semantics to highlight several key design choices.
%
\teo{Make this true:}
First, we note that the life cycle rules (in combination with the definition rules) prevent programs that read and write to values within a loop except in the narrow circumstance of updates, which cannot even be applied to scalar definitions.
%
Beyond the simple management of iterator state, these rules allow us to effectively analyze the propagation of constants within a loop.
%
We eliminate problems that in a less restrictive language would require alias analysis so that we can tell when a zero or repetitive value read from one tensor is being used in an expression or written to another tensor.
%
These restrictions play a similar role to that of a pure function in Halide~\cite{ragan-kelley_halide_2013}.
%
Second, loops with tensor accesses enter into a looplet system via the Unfurl rule.
%
In this system, repeated structures (Run) and constant information (Switch)  are slowly uncovered as accesses are lowered.
%
In this process, we are able to use rewrite rules (Simplify) to eliminate cases, unnecessary iterations, and so forth
